Structural Divergence Analysis

### 2017-05-10 comparison_R0.Rmd
charla 11-5-17

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, CN)
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, CN)

cor.df = data.frame("Comparison R0.1" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

## calculate corelations
r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("Comparison R0.1" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, CN)
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, CN)

cor.df = data.frame("Comparison R0.2" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

## calculate corelations
r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("Comparison R0.2" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

# calculate cors
r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)

# save data
R0.1.mean.exp = d.exp$median.Pn
R0.1.mean.mut = d.mut$median.Pn
R0.1.mean.medium = d.medium$median.Pn

@@

# calculate cors
r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)

# save data
R0.2.mean.exp = d.exp$median.Pn
R0.2.mean.mut = d.mut$median.Pn
R0.2.mean.medium = d.medium$median.Pn

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)

# save data
R0.1.mean.exp = d.exp$mean.nH
R0.1.mean.mut = d.mut$mean.nH
R0.1.mean.medium = d.medium$mean.nH

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)

# save data
R0.2.mean.exp = d.exp$mean.nH
R0.2.mean.mut = d.mut$mean.nH
R0.2.mean.medium = d.medium$mean.nH

>>>>

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("Comparison R0.1" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

## calculate corelations
r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("Comparison R0.1" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("Comparison R0.2" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

@@

## calculate corelations
r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
r.score.CN = cor(score, log(CN))

cor.df = data.frame("Comparison R0.2" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

@@

# calculate cors
r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])

# save data
R0.1.mean.exp = d.exp$median.Pn[1:100]
R0.1.mean.mut = d.mut$median.Pn[1:100]
R0.1.mean.medium = d.medium$median.Pn[1:100]

@@

# calculate cors
r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])

# save data
R0.2.mean.exp = d.exp$median.Pn[1:100]
R0.2.mean.mut = d.mut$median.Pn[1:100]
R0.2.mean.medium = d.medium$median.Pn[1:100]

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])

# save data
R0.1.mean.exp = d.exp$mean.nH[1:100]
R0.1.mean.mut = d.mut$mean.nH[1:100]
R0.1.mean.medium = d.medium$mean.nH[1:100]

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])

# save data
R0.2.mean.exp = d.exp$mean.nH[1:100]
R0.2.mean.mut = d.mut$mean.nH[1:100]
R0.2.mean.medium = d.medium$mean.nH[1:100]
